Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond

### 2024-02-11 outputs/paper/paper.qmd
Update paper.qmd

## Features
From now on, every white refers to non-Hispanic, caucassian. Every black refers to non-Hispanic, African American. Hispanic refers to people with Hispanic ethinicity majority from south America.

# Results
The results section should convey findings.
## Table, graph, table, graph

## Source
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-bratetrend-graph
#| fig-cap: "Trend in US Birth Rates"

@@

Also, we should not disregard the fact that for all statistical data, they always going to be a missing value that is not properly collected. A lot of people might not just report or illegally keep the population due to their illegal status in the US.

>>>>

## Features
De facto population of women of reproductive age is 15 to 49 years in a country (WHO 2024). The average age of the final menstrual period (menopause) is age 51, women age in 40s, pregnancy is rare but not impossible (asrm 2012). Beginning in 1997, the birth rate for the maternal age group 45-49 includes data for mothers aged 45 and over in the numerator and is based on the population of women aged 45-49 in the denominator (National Center for Health Statistics 2023). Thus the women population in the age group 45-49 is eliminated in this paper although they fall under the reproductive age group category in a country. Birth data is comprised of births per 1,000 women age 15 to 44 over the 40 years period from 1980 to 2020.
For the race and ethnicity, every white refers to non-Hispanic, caucassian population group. Every black refers to non-Hispanic, African American group. Hispanic refers to people with Hispanic ethinicity majority from south America to abberiviate.

# Results

## Trend in US Birth Rates
The overall trend fluctuates from time to time but the highest births moment is recorded as in 1991 for the rate of 71

## Trends in Birth Rates by Population Subgroup

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-bratetrend-graph
#| fig-cap: "Trend in US Birth Rates"

@@
